---
title: "R_script_for_quality_checks_of_cleaned_database"
author: "Clare McDonald & Viveka Hall-Holt"
date: "1/8/2021"
output: html_document
---

```{r setup, include = FALSE} 
library(tidyverse)
library(dplyr)
library(mosaic)
library(psych)
covid_data <- read_csv("~/Stony Brook Research/COVID_19_December_2020_Cleaned_Data.csv")
```

<<<<<<< HEAD
Example of format:
```{r}
##Name of item/score
# Frequency Distributions (mean/sd)

# Histogram 

# Verification of Variable Coding (Range)

# Scale Reliability

```

=======
# Demographics
```{r}
##Demographics_age
# Frequency Distributions (mean/sd, n per scale)
covid_data$Demographics_age <- as.numeric(as.character(covid_data$Demographics_age))
favstats(~ Demographics_age, data = covid_data)#[c("mean","sd","n","missing")]
#length(covid_data$Demographics_age)-sum(is.na(covid_data$Demographics_age))

# Histogram 
hist(covid_data$Demographics_age)

#length(covid_data$Demographics_age)-sum(is.na(covid_data$Demographics_age)) 

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_gender
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_gender, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_gender)

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_ethnicity
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_ethnicity, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_ethnicity)

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_political_general
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_political_general, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_political_general)

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_societal
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_societal, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_societal)

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_economic
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_economic, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_economic)

# Verification of Variable Coding (Range)
```

```{r}
##Demographics_economic
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Demographics_economic, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Demographics_economic)

# Verification of Variable Coding (Range)
```

# Green Short Scores
```{r}
##Green_PartA_short_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_PartA_short_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_PartA_short_score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(Green_Short_A1, Green_Short_A2, Green_Short_A3, Green_Short_A4, Green_Short_A5, Green_Short_A6,
         Green_Short_A7, Green_Short_A8) %>%
  alpha()
```

```{r}
##Green_PartB_short_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_PartB_short_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_PartB_short_score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(Green_Short_B1, Green_Short_B2, Green_Short_B3, Green_Short_B4,
         Green_Short_B5, Green_Short_B6, Green_Short_B7, Green_Short_B8, Green_Short_B9, Green_Short_B10) %>%
  alpha()

```

```{r}
##Green_Total_Short_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Total_Short_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Total_Short_Score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(Green_Short_A1, Green_Short_A2, Green_Short_A3, Green_Short_A4, Green_Short_A5, Green_Short_A6,
         Green_Short_A7, Green_Short_A8, Green_Short_B1, Green_Short_B2, Green_Short_B3, Green_Short_B4,
         Green_Short_B5, Green_Short_B6, Green_Short_B7, Green_Short_B8, Green_Short_B9, Green_Short_B10) %>%
  alpha()
```

# IUS Scores
```{r}
##IUS_Inhibitory_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Inhibitory_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Inhibitory_score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(IUS_Short_8, IUS_Short_9, IUS_Short_10, IUS_Short_10, IUS_Short_11, IUS_Short_12) %>%
  alpha()
```

```{r}
##IUS_Prospective_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Prospective_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Prospective_score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(IUS_Short_1, IUS_Short_2, IUS_Short_3, IUS_Short_4, IUS_Short_5, IUS_Short_6, IUS_Short_7) %>%
  alpha()
```

```{r}
##IUS_Total_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Total_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Total_Score)

# Scale Reliability
covid_data %>%
  dplyr::select(IUS_Short_1, IUS_Short_2, IUS_Short_3, IUS_Short_4, IUS_Short_5, IUS_Short_6, IUS_Short_7,
         IUS_Short_8, IUS_Short_9, IUS_Short_10, IUS_Short_10, IUS_Short_11, IUS_Short_12) %>%
  alpha()
```

<<<<<<< HEAD
=======
# GCBS
```{r}
##GCBS_gm
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_gm, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_gm)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_1, World_Beliefs_6, World_Beliefs_11) %>%
  alpha()
```

```{r}
##GCBS_et
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_et, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_et)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_2, World_Beliefs_7, World_Beliefs_12) %>%
  alpha()
```

```{r}
##GCBS_mg
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_mg, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_mg)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_3, World_Beliefs_8, World_Beliefs_13) %>%
  alpha()

```

```{r}
##GCBS_pw
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_pw, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_pw)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_4, World_Beliefs_9, World_Beliefs_14) %>%
  alpha()

```

```{r}
##GCBS_ci
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_ci, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_ci)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_5, World_Beliefs_10, World_Beliefs_15) %>%
  alpha()
```

```{r}
##GCBS_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ GCBS_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$GCBS_total)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(World_Beliefs_1, World_Beliefs_2, World_Beliefs_3, World_Beliefs_4, World_Beliefs_5, World_Beliefs_6,
         World_Beliefs_7, World_Beliefs_8, World_Beliefs_9, World_Beliefs_10, World_Beliefs_11,
         World_Beliefs_12, World_Beliefs_13, World_Beliefs_14, World_Beliefs_15) %>%
  alpha()

```

# MIS_total
```{r}
##MIS_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ MIS_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$MIS_total)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
  dplyr::select(MIS_1, MIS_2, MIS_3, MIS_4, MIS_5, MIS_6, MIS_7, MIS_8, MIS_9, MIS_10, MIS_11, MIS_12,
         MIS_13, MIS_14, MIS_15) %>%
  alpha()
```

# PAS
```{r}
##PAS_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ PAS_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$PAS_total)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
  dplyr::select(PAS_1, PAS_2, PAS_3, PAS_4, PAS_5, PAS_6, PAS_7, PAS_8, PAS_9, PAS_10, PAS_11, PAS_12,
         PAS_13, PAS_14, PAS_15) %>%
  alpha()
```

# Social_Anhedonia
```{r}
##Social_Anhedonia_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Social_Anhedonia_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Social_Anhedonia_Score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
  dplyr::select(R_SAS_1, R_SAS_2, R_SAS_3, R_SAS_4, R_SAS_5, R_SAS_6, R_SAS_7, R_SAS_8, R_SAS_9, R_SAS_10,
         R_SAS_11, R_SAS_12, R_SAS_13, R_SAS_14, R_SAS_15) %>%
  alpha()
```

# PhAnS
```{r}
##PhAnS_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ PhAnS_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$PhAnS_score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(PhAnS_1, PhAnS_2, PhAnS_3, PhAnS_4, PhAnS_5, PhAnS_6, PhAnS_7, PhAnS_8, PhAnS_9, PhAnS_10,
         PhAnS_11, PhAnS_12, PhAnS_13, PhAnS_14, PhAnS_15) %>%
  alpha()
```

#Sxtypy
don't think we need scale reliability for these -- i'll ask
```{r}
##pos_sxtypy_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ pos_sxtypy_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$pos_sxtypy_total)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##neg_sxtypy_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ neg_sxtypy_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$neg_sxtypy_total)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##overall_sxtypy_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ overall_sxtypy_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$overall_sxtypy_total)

# Verification of Variable Coding (Range)

# Scale Reliability

```

#STAIT
```{r}
##STAIT_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ STAIT_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$STAIT_total)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(STAIT_1, STAIT_2, STAIT_3, STAIT_4, STAIT_5, STAIT_6, STAIT_7,
           STAIT_8, STAIT_9, STAIT_10, STAIT_11, STAIT_12, STAIT_13, STAIT_14, STAIT_15,
           STAIT_16, STAIT_17, STAIT_18, STAIT_19, STAIT_20) %>%
  alpha()
```

# STAIS
```{r}
##STAIS_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ STAIS_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$STAIS_total)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(STAIS_1, STAIS_2, STAIS_3, STAIS_4, STAIS_5, STAIS_6, STAIS_7,
           STAIS_8, STAIS_9, STAIS_10, STAIS_11, STAIS_12, STAIS_13, STAIS_14, STAIS_15,
           STAIS_16, STAIS_17, STAIS_18, STAIS_19, STAIS_20) %>%
  alpha()
```

# PSWQ
```{r}
##STAIS_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ PSWQ_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$PSWQ_total)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(PSWQ_1, PSWQ_2, PSWQ_3, PSWQ_4, PSWQ_5, PSWQ_6, PSWQ_7, PSWQ_8,
           PSWQ_9, PSWQ_10, PSWQ_11, PSWQ_12, PSWQ_13, PSWQ_14, PSWQ_15, PSWQ_16) %>%
  alpha()
```

# COVID_conspiracies
```{r}
##COVID_conspiracies_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conspiracies_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conspiracies_total)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
 dplyr::select(COVID_19_3_1, COVID_19_3_2, COVID_19_3_3, 
             COVID_19_3_4, COVID_19_3_5, COVID_19_3_6, COVID_19_3_7, COVID_19_3_8,  
             COVID_19_3_9, COVID_19_3_10, COVID_19_3_11, COVID_19_3_12, COVID_19_3_13,
             COVID_19_3_14, COVID_19_3_15, COVID_19_3_16) %>%
  alpha()

```

```{r}
##Conspiracies_endorsed
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Conspiracies_endorsed, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Conspiracies_endorsed)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_3_1_true, COVID_19_3_2_true, COVID_19_3_3_true, 
             COVID_19_3_4_true, COVID_19_3_5_true, COVID_19_3_6_true, COVID_19_3_7_true,
             COVID_19_3_8_true, COVID_19_3_9_true, COVID_19_3_10_true, COVID_19_3_11_true,
             COVID_19_3_12_true, COVID_19_3_13_true, COVID_19_3_14_true, COVID_19_3_15_true, COVID_19_3_16_true) %>%
  alpha()

```

```{r}
##Conspiracies_endorsed_lgtrans
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Conspiracies_endorsed_lgtrans, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Conspiracies_endorsed_lgtrans)

# Verification of Variable Coding (Range)
```

```{r}
##COVID_factsvmisinfo_score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_factsvmisinfo_score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_factsvmisinfo_score)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
 dplyr::select(Facts_vs_misinfo_1, Facts_vs_misinfo_2, Facts_vs_misinfo_3,
           Facts_vs_misinfo_4, Facts_vs_misinfo_5, Facts_vs_misinfo_6, Facts_vs_misinfo_7, 
           Facts_vs_misinfo_8, Facts_vs_misinfo_9, Facts_vs_misinfo_10, Facts_vs_misinfo_11, 
           Facts_vs_misinfo_12, Facts_vs_misinfo_13, Facts_vs_misinfo_14, Facts_vs_misinfo_15, 
           Facts_vs_misinfo_16) %>%
  alpha()
```

# Health_Behavior
```{r}
##Health_Behavior_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Health_Behavior_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Health_Behavior_Score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(Health_Behavior_1, Health_Behavior_1a, Health_Behavior_2,
           Health_Behavior_2a, Health_Behavior_3, Health_Behavior_4, Health_Behavior_5,
           Health_Behavior_6, Health_Behavior_7, Health_Behavior_8) %>%
  alpha()
```

# COVID_conseq
```{r}
##COVID_conseq_sxs
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_sxs, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_sxs)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_1_Headache, COVID_19_2_1_Fever, COVID_19_2_1_Bodyache,
              COVID_19_2_1_Fatigue, COVID_19_2_1_Neckpain, COVID_19_2_1_Lossofsleep, 
              COVID_19_2_1_Lossofappetite, COVID_19_2_1_Cough, COVID_19_2_1_Sorethroat,
           COVID_19_2_1_Nasalcongestion, COVID_19_2_1_Breathingproblems) %>%
  alpha()

```

```{r}
##COVID_conseq_abilities
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_abilities, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_abilities)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_2_getoutofbed, COVID_19_2_2_preparemeals,
              COVID_19_2_2_performdailyroutines, COVID_19_2_2_leavehome,
              COVID_19_2_2_concentrateonwork, COVID_19_2_2_completemywork) %>%
  alpha()

```

```{r}
##COVID_conseq_mood
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_mood, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_mood)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_Irritable, COVID_19_2_Worried, COVID_19_2_Helpless, 
              COVID_19_2_Frustrated) %>%
  alpha()

```

```{r}
##COVID_conseq_burden_to_others
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_burden_to_others, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_burden_to_others)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_makingthemworry, COVID_19_2_beingaburden, 
              COVID_19_2_limitingtheirlives, COVID_19_2_needingtodependonthem,  
              COVID_19_2_takecareofpeople, COVID_19_2_spreadinginfectiontothem) %>%
  alpha()

```

```{r}
##COVID_conseq_realworld
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_realworld, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_realworld)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_sufferfinancially, COVID_19_2_personalrelationships,
              COVID_19_2_foodandhousing) %>%
  alpha()

```

```{r}
##COVID_conseq_total
# Frequency Distributions (mean/sd, n per scale)
favstats(~ COVID_conseq_total, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$COVID_conseq_total)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(COVID_19_2_1_Headache, COVID_19_2_1_Fever, COVID_19_2_1_Bodyache,
              COVID_19_2_1_Fatigue, COVID_19_2_1_Neckpain, COVID_19_2_1_Lossofsleep, 
              COVID_19_2_1_Lossofappetite, COVID_19_2_1_Cough, COVID_19_2_1_Sorethroat,
              COVID_19_2_1_Nasalcongestion, COVID_19_2_1_Breathingproblems, 
              COVID_19_2_2_getoutofbed, COVID_19_2_2_preparemeals,
              COVID_19_2_2_performdailyroutines, COVID_19_2_2_leavehome,
              COVID_19_2_2_concentrateonwork, COVID_19_2_2_completemywork,
              COVID_19_2_Irritable, COVID_19_2_Worried, COVID_19_2_Helpless, 
              COVID_19_2_Frustrated, COVID_19_2_makingthemworry, COVID_19_2_beingaburden, 
              COVID_19_2_limitingtheirlives, COVID_19_2_needingtodependonthem,  
              COVID_19_2_takecareofpeople, COVID_19_2_spreadinginfectiontothem,
              COVID_19_2_sufferfinancially, COVID_19_2_personalrelationships,
              COVID_19_2_foodandhousing) %>%
  alpha()

```

# Perceived_Infectability
```{r}
##Perceived_Infectability
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Perceived_Infectability, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Perceived_Infectability)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
 dplyr::select(PVDS_8, PVDS_12, PVDS_2, PVDS_14, PVDS_10, PVDS_5, PVDS_6) %>%
  alpha()

```

# Germ_Aversion
```{r}
##Germ_Aversion
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Germ_Aversion, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Germ_Aversion)

# Verification of Variable Coding (Range)

# Scale Reliability

covid_data %>%
 dplyr::select(PVDS_7, PVDS_15, PVDS_4, PVDS_9, PVDS_3, PVDS_1, PVDS_13, PVDS_11) %>%
  alpha()

```

# Rotters
```{r}
##Rotters_general
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Rotters_general, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Rotters_general)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(RLOC_5, RLOC_9, RLOC_11, RLOC_13, RLOC_15, RLOC_16 + 
                           RLOC_18, RLOC_25, RLOC_28) %>%
  alpha()

```

```{r}
##Rotters_political
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Rotters_political, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Rotters_political)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(RLOC_3, RLOC_12, RLOC_17, RLOC_22) %>%
  alpha()

```

```{r}
##RLOC_Total_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ RLOC_Total_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$RLOC_Total_Score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(RLOC_2, RLOC_3, RLOC_4, RLOC_5, RLOC_6, RLOC_7, RLOC_9, 
                 RLOC_10, RLOC_11, RLOC_12, RLOC_13, RLOC_15,
                 RLOC_16, RLOC_17, RLOC_18, RLOC_20, RLOC_21,
                 RLOC_23, RLOC_25, RLOC_26, RLOC_28, RLOC_29) %>%
  alpha()
```

# NFCS
```{r}
##NFCS_Total_Score
# Frequency Distributions (mean/sd, n per scale)
favstats(~ NFCS_Total_Score, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$NFCS_Total_Score)

# Verification of Variable Coding (Range)

# Scale Reliability
covid_data %>%
 dplyr::select(NFCS_1, NFCS_2, NFCS_3, NFCS_4, NFCS_5, NFCS_6, NFCS_7, 
               NFCS_8, NFCS_9, NFCS_10, NFCS_11, NFCS_12, NFCS_13, NFCS_14, NFCS_15) %>%
  alpha()

```

# CRT?

# Individual Items
# World Beliefs
```{r}
##World_Beliefs_1
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_1, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_1)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_2
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_2, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_2)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_3
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_2, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_3)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_4
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_4, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_4)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_5
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_5, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_5)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_6
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_6, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_6)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_7
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_7, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_7)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_8
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_8, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_8)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_9
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_9, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_9)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_10
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_10, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_10)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_11
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_11, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_11)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_12
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_12, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_12)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_13
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_13, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_13)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_14
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_14, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_14)

# Verification of Variable Coding (Range)

# Scale Reliability

```

```{r}
##World_Beliefs_15
# Frequency Distributions (mean/sd, n per scale)
favstats(~ World_Beliefs_15, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$World_Beliefs_15)

# Verification of Variable Coding (Range)

# Scale Reliability

```

# Green Short
```{r}
##Green_Short_A1
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A1, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A1)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A2
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A2, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A2)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A3
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A3, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A3)

# Verification of Variable Coding (Range)

```


```{r}
##Green_Short_A4
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A4, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A4)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A5
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A5, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A5)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A6
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A6, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A6)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A7
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A7, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A7)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_A8
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_A8, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_A8)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B1
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B1, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B1)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B2
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B2, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B2)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B3
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B3, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B3)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B4
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B4, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B4)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B5
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B5, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B5)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B6
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B6, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B6)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B7
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B7, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B7)

# Verification of Variable Coding (Range)


```

```{r}
##Green_Short_B8
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B8, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B8)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B9
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B9, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B9)

# Verification of Variable Coding (Range)

```

```{r}
##Green_Short_B10
# Frequency Distributions (mean/sd, n per scale)
favstats(~ Green_Short_B10, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$Green_Short_B10)

# Verification of Variable Coding (Range)

```

# IUS Short
```{r}
##IUS_Short_1
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_1, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_1)

# Verification of Variable Coding (Range)

```

```{r}
##IUS_Short_2
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_2, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_2)

# Verification of Variable Coding (Range)

```

```{r}
##IUS_Short_3
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_3, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_3)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_4
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_4, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_4)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_5
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_5, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_5)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_6
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_6, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_6)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_7
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_7, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_7)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_8
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_8, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_8)

# Verification of Variable Coding (Range)
```

```{r}
##IUS_Short_9
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_9, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_9)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_10
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_10, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_10)

# Verification of Variable Coding (Range)


```

```{r}
##IUS_Short_11
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_11, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_11)

# Verification of Variable Coding (Range)

```

```{r}
##IUS_Short_12
# Frequency Distributions (mean/sd, n per scale)
favstats(~ IUS_Short_12, data = covid_data)#[c("mean","sd","n","missing")]

# Histogram 
hist(covid_data$IUS_Short_12)

# Verification of Variable Coding (Range)

```

# Counting NAs in each column

```{r, eval = FALSE}
# deleted column by column code to save space
colSums(is.na(covid_data))

#CRT not as consistent (294, 298, 295 x 4, 297; 4)
#World Beliefs consistent (72 x 5,  71 x 3, 72, 71 x 6; 1)
#Green Short consistent (71 x 8, 72, 71 x 3, 72, 71 x 2, 72 x 2, 71; 1)
#IUS consistent (359 x 12; 0)
#MIS consistent (96 x 8, 97, 96 x 5; 1)
#PAS consistent (69 x 15; 0)
#R_SAS consistent (86 x 15; 0)
#PhAnS consistent (72 x 2, 73, 72 x 9, 73, 72 x 2; 1)
#STAIT consistent (64 x 3, 65 x 9, 66, 65 x 2; 2)
#STAIS consistent (84 x 12, 86, 84 x 2, 85, 84 x 4; 2)
#PSWQ consistent (77 x 3, 78, 77 x 12)
#COVID_19_3 consistent (86 x 13, 87, 86 x 2; 1)
#Attitudes/Behaviors not totally consistent (66 x 8, 88, 66, 69 x 2; 22!)
#Health_Behavior consistent (except for questions 7-9 which were added later) (72 x 8 and 337 x 3; 0 and 0)
#Covid-19_1 consistent (88 x 3, 89, 88 x 9; 1)
#Covid_19_2 consistent (70 x 4, 71, 70 x 25; 1)
#PVDS consistent (81 x 15; 0)
#RLOC consistent (353 x 9, 355 x 2, 354 x 3, 355 x 2, 354, 353 x 3, 354 x 5, 353 x 4; 2)
#NFCS consistent (354 x 2, 353 x 4, 354, 353 x 8; 1)
```
