---
title: "Stony Brook Data Cleaning"
author: "Clare McDonald & Viveka Hall-Holt"
date: "12/2/2020"
output: pdf_document
---

```{r setup, include = FALSE} 
library(tidyverse)
library(dplyr)
covid_data <- read_csv("~/Stony Brook Research/COVID-19_December 14, 2020_14.40 .csv")
```

# Deleting First Row from each column
It was irrelevant and messed with classification of variables
```{r}
covid_data <- covid_data %>% 
   filter(row_number() > (n() - 673))
# note - remember to delete spring participants, ask Megan what specifically should be done
# thanks!
```

# Green Variables
```{r}
# Renaming Green variables
covid_data <- covid_data %>%
  rename(Green_Short_A1 = "R-GPTS_Ref_1",
         Green_Short_A2 = "R-GPTS_Ref_2",
         Green_Short_A3 = "R-GPTS_Ref_3",
         Green_Short_A4 = "R-GPTS_Ref_4",
         Green_Short_A5 = "R-GPTS_Ref_5",
         Green_Short_A6 = "R-GPTS_Ref_6",
         Green_Short_A7 = "R-GPTS_Ref_7",
         Green_Short_A8 = "R-GPTS_Ref_8",
         Green_Short_B1 = "R-GPTS_Per_1",
         Green_Short_B2 = "R-GPTS_Per_2",
         Green_Short_B3 = "R-GPTS_Per_3",
         Green_Short_B4 = "R-GPTS_Per_4",
         Green_Short_B5 = "R-GPTS_Per_5",
         Green_Short_B6 = "R-GPTS_Per_6",
         Green_Short_B7 = "R-GPTS_Per_7",
         Green_Short_B8 = "R-GPTS_Per_8",
         Green_Short_B9 = "R-GPTS_Per_9",
         Green_Short_B10 = "R-GPTS_Per_10")

# fixed renaming up here and just got rid of the "w" originally. thanks for noticing that!
#messing around with learning how to make loops. disregard.
#for (n in 1:8) {
#covid_data <- covid_data %>% rename(sym(paste("Green_Short_A", n, sep="")) = paste("R-GPTS_Ref_", n, sep=""))
#}
#n = 2
#covid_data <- covid_data %>% rename(Green_Short_A2 = "R-GPTS_Ref_2")
#names(covid_data)[ names(covid_data) == paste0("NFCS_", 1) ] = "OK"
```

```{r}
# Recoding Green variables
covid_data <- covid_data %>%
  mutate(Green_Short_A1 = fct_recode(Green_Short_A1, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_A2 = fct_recode(Green_Short_A2, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_A3 = fct_recode(Green_Short_A3, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_A4 = fct_recode(Green_Short_A4, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),  
         Green_Short_A5 = fct_recode(Green_Short_A5, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),  
         Green_Short_A6 = fct_recode(Green_Short_A6, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),  
         Green_Short_A7 = fct_recode(Green_Short_A7, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"), 
         Green_Short_A8 = fct_recode(Green_Short_A8, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_B1 = fct_recode(Green_Short_B1, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_B2 = fct_recode(Green_Short_B2, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_B3 = fct_recode(Green_Short_B3, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_B4 = fct_recode(Green_Short_B4, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_B5 = fct_recode(Green_Short_B5, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_B6 = fct_recode(Green_Short_B6, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),   
         Green_Short_B7 = fct_recode(Green_Short_B7, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),               
         Green_Short_B8 = fct_recode(Green_Short_B8, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_B9 = fct_recode(Green_Short_B9, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"),
         Green_Short_B10 = fct_recode(Green_Short_B10, 
                                      "0" = "1", "1" = "2", "2" = "3", "3" = "4", "4" = "5"))
# issue - recoding these as factors turns them into character variables
# we can deal with this later after removing NAs and weird values
# sounds good. do you know how to reverse them from being character variables?
# use parse_integer command (see below or google doc)
```

```{r}
# use this reduced dataset to calculate green scores. by removing NAs, the data recodes into a factor class which works for calculations I think. But I don't think we want to remove NAs generally, because it gets rid of all that persons responses for all scales, which is why I made a separate dataset for it 
covid_data_calc_green <- covid_data %>%
  filter(!is.na(Green_Short_A1w)) 
```

#Make Green NA until June 17
```{r}
for (n in 1:8)
     covid_data[[paste0("Green_Short_A", n)]] <- replace(covid_data[[paste0("Green_Short_A", n)]], 1:300, NA)

for (n in 1:10)
      covid_data[[paste0("Green_Short_B", n)]] <- replace(covid_data[[paste0("Green_Short_B", n)]], 1:300, NA)

#loop to replace June 4-17 for Green Short
#for (n in 1:8)
#     covid_data[[paste0("Green_Short_A", n)]] <- replace(covid_data[[paste0("Green_Short_A", n)]], 274:300, NA)

#for (n in 1:10)
#     covid_data[[paste0("Green_Short_B", n)]] <- replace(covid_data[[paste0("Green_Short_B", n)]], 274:300, NA)

#for (i in c(Green_Short_A1, Green_Short_A2, Green_Short_A3, Green_Short_A4, Green_Short_A5, Green_Short_A6, Green_Short_A7, Green_Short_A8, Green_Short_B1, Green_Short_B2, Green_Short_B3, Green_Short_B4, Green_Short_B5, Green_Short_B6, Green_Short_B7, Green_Short_B8, Green_Short_B9, Green_Short_B10)) {
#    for (j in 273<row.names(covid_data<301)) {
#        fct_recode(j, 
#                                      "0" = "NA", "1" = "NA", "2" = "NA", "3" = "NA", "4" = "NA")
#    }
```

#Short Version Scoring for Green Paranoia
```{r}
#Green Part A score
#all of my ideas are not working but I'll get it eventually!
#covid_data %>%
#mutate(Green_PartA_short_score = Green_Short_A1)

#covid_data %>% mutate("Green_Short_A1") = parse_integer(as.character("Green_Short_A1"))
                                                         
#covid_data %>%
#for (n in 1:8)
  #mutate(sym(paste0("Green_Short_A", n)) = parse_integer(as.character(paste0("Green_Short_A", n))


#covid_data %>%
#mutate(Green_PartA_short_score = 
        # for (n in 1:8) 
         # Green_PartA_short_score + paste0("Green_Short_A", n)
          # )

#covid_data$Green_PartA_short_score <- 0
#covid_data$Green_PartA_short_score <- covid_data$Green_PartA_short_score + covid_data$Green_Short_A1

#Green Part B score

```

#IUS (short form)
```{r}
#Short Version Scoring for IUS
#Inhibitory Anxiety Scoring

#Prospective Anxiety Scoring

##Make IUS NA until June 17
for (n in 1:12)
     covid_data[[paste0("IUS_Short_", n)]] <- replace(covid_data[[paste0("IUS_Short_", n)]], 1:300, NA)
```

#Demographics
```{r}
#Rename variables
covid_data <- covid_data %>%
  rename(Demographics_age = "1)",
         Demographics_gender = "2)",
         Demographics_gender_text = "2)_6_TEXT",
         Demographics_ethnicity = "3)",
         Demographics_ethnicity_text = "3)_8_TEXT")

```

# Magical Ideation
```{r}
# recoding
covid_data <- covid_data %>%
  mutate(MIS_1 = fct_recode(MIS_1, "0" = "2"),
         MIS_2 = fct_recode(MIS_2, "0" = "2"),
         MIS_3 = fct_recode(MIS_3, "0" = "2"),
         MIS_4 = fct_recode(MIS_4, "0" = "2"),
         MIS_5 = fct_recode(MIS_5, "0" = "2"),
         MIS_6 = fct_recode(MIS_6, "0" = "2"),
         MIS_7 = fct_recode(MIS_7, "0" = "2"),
         MIS_8 = fct_recode(MIS_8, "0" = "2"),
         MIS_9 = fct_recode(MIS_9, "0" = "2"),
         MIS_10 = fct_recode(MIS_10, "0" = "2"),
         MIS_12 = fct_recode(MIS_12, "0" = "2"),
         MIS_13 = fct_recode(MIS_13, "0" = "2"),
         MIS_14 = fct_recode(MIS_14, "0" = "2"),
         MIS_15 = fct_recode(MIS_15, "0" = "2"),
         MIS_11 = fct_recode(MIS_11, "0" = "1", "1" = "2"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(MIS_1 = parse_integer(as.character(MIS_1)),
         MIS_2 = parse_integer(as.character(MIS_2)),
         MIS_3 = parse_integer(as.character(MIS_3)),
         MIS_4 = parse_integer(as.character(MIS_4)),
         MIS_5 = parse_integer(as.character(MIS_5)),
         MIS_6 = parse_integer(as.character(MIS_6)),
         MIS_7 = parse_integer(as.character(MIS_7)),
         MIS_8 = parse_integer(as.character(MIS_8)),
         MIS_9 = parse_integer(as.character(MIS_9)),
         MIS_10 = parse_integer(as.character(MIS_10)),
         MIS_11 = parse_integer(as.character(MIS_11)),
         MIS_12 = parse_integer(as.character(MIS_12)),
         MIS_13 = parse_integer(as.character(MIS_13)),
         MIS_14 = parse_integer(as.character(MIS_14)),
         MIS_15 = parse_integer(as.character(MIS_15)))
covid_data <- covid_data %>%
  mutate(MIS_total = MIS_1 + MIS_2 + MIS_3 + MIS_4 + MIS_5 + MIS_6 + MIS_7 + MIS_8 + MIS_9 + MIS_10 + MIS_11 +
         MIS_12 + MIS_13 + MIS_14 + MIS_15)
```

# Perceptual Aberration Scale
```{r}
# recoding
covid_data <- covid_data %>%
  mutate(PAS_1 = fct_recode(PAS_1, "0" = "2"),
         PAS_2 = fct_recode(PAS_2, "0" = "2"),
         PAS_3 = fct_recode(PAS_3, "0" = "2"),
         PAS_4 = fct_recode(PAS_4, "0" = "2"),
         PAS_5 = fct_recode(PAS_5, "0" = "2"),
         PAS_6 = fct_recode(PAS_6, "0" = "2"),
         PAS_7 = fct_recode(PAS_7, "0" = "2"),
         PAS_8 = fct_recode(PAS_8, "0" = "2"),
         PAS_9 = fct_recode(PAS_9, "0" = "2"),
         PAS_10 = fct_recode(PAS_10, "0" = "2"),
         PAS_11 = fct_recode(PAS_11, "0" = "2"),
         PAS_12 = fct_recode(PAS_12, "0" = "2"),
         PAS_13 = fct_recode(PAS_13, "0" = "2"),
         PAS_14 = fct_recode(PAS_14, "0" = "2"),
         PAS_15 = fct_recode(PAS_15, "0" = "2"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(PAS_1 = parse_integer(as.character(PAS_1)),
         PAS_2 = parse_integer(as.character(PAS_2)),
         PAS_3 = parse_integer(as.character(PAS_3)),
         PAS_4 = parse_integer(as.character(PAS_4)),
         PAS_5 = parse_integer(as.character(PAS_5)),
         PAS_6 = parse_integer(as.character(PAS_6)),
         PAS_7 = parse_integer(as.character(PAS_7)),
         PAS_8 = parse_integer(as.character(PAS_8)),
         PAS_9 = parse_integer(as.character(PAS_9)),
         PAS_10 = parse_integer(as.character(PAS_10)),
         PAS_11 = parse_integer(as.character(PAS_11)),
         PAS_12 = parse_integer(as.character(PAS_12)),
         PAS_13 = parse_integer(as.character(PAS_13)),
         PAS_14 = parse_integer(as.character(PAS_14)),
         PAS_15 = parse_integer(as.character(PAS_15)))
covid_data <- covid_data %>%
  mutate(PAS_total = PAS_1 + PAS_2 + PAS_3 + PAS_4 + PAS_5 + PAS_6 + PAS_7 + PAS_8 + PAS_9 + PAS_10 + PAS_11 +
           PAS_12 + PAS_13 + PAS_14 + PAS_15)
```

# Revised Social Anhedonia Scale
```{r}
# recoding variables
covid_data <- covid_data %>%
  mutate(R_SAS_1 = fct_recode(R_SAS_1, "0" = "2"),
         R_SAS_2 = fct_recode(R_SAS_2, "0" = "2"),
         R_SAS_3 = fct_recode(R_SAS_3, "0" = "2"),
         R_SAS_5 = fct_recode(R_SAS_5, "0" = "2"),
         R_SAS_6 = fct_recode(R_SAS_6, "0" = "2"),
         R_SAS_7 = fct_recode(R_SAS_7, "0" = "2"),
         R_SAS_8 = fct_recode(R_SAS_8, "0" = "2"),
         R_SAS_10 = fct_recode(R_SAS_10, "0" = "2"),
         R_SAS_15 = fct_recode(R_SAS_15, "0" = "2"),
         R_SAS_4 = fct_recode(R_SAS_4, "0" = "1", "1" = "2"),
         R_SAS_9 = fct_recode(R_SAS_9, "0" = "1", "1" = "2"),
         R_SAS_11 = fct_recode(R_SAS_11, "0" = "1", "1" = "2"),
         R_SAS_12 = fct_recode(R_SAS_12, "0" = "1", "1" = "2"),
         R_SAS_13 = fct_recode(R_SAS_13, "0" = "1", "1" = "2"),
         R_SAS_14 = fct_recode(R_SAS_14, "0" = "1", "1" = "2"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(R_SAS_1 = parse_integer(as.character(R_SAS_1)),
         R_SAS_2 = parse_integer(as.character(R_SAS_2)),
         R_SAS_3 = parse_integer(as.character(R_SAS_3)),
         R_SAS_4 = parse_integer(as.character(R_SAS_4)),
         R_SAS_5 = parse_integer(as.character(R_SAS_5)),
         R_SAS_6 = parse_integer(as.character(R_SAS_6)),
         R_SAS_7 = parse_integer(as.character(R_SAS_7)),
         R_SAS_8 = parse_integer(as.character(R_SAS_8)),
         R_SAS_9 = parse_integer(as.character(R_SAS_9)),
         R_SAS_10 = parse_integer(as.character(R_SAS_10)),
         R_SAS_11 = parse_integer(as.character(R_SAS_11)),
         R_SAS_12 = parse_integer(as.character(R_SAS_12)),
         R_SAS_13 = parse_integer(as.character(R_SAS_13)),
         R_SAS_14 = parse_integer(as.character(R_SAS_14)),
         R_SAS_15 = parse_integer(as.character(R_SAS_15)))
covid_data <- covid_data %>%
  mutate(Social_Anhedonia_Score = R_SAS_1 + R_SAS_2 + R_SAS_3 + R_SAS_4 + R_SAS_5 + R_SAS_6 + R_SAS_7 +
           R_SAS_8 + R_SAS_9 + R_SAS_10 + R_SAS_11 + R_SAS_12 + R_SAS_13 + R_SAS_14 + R_SAS_15)
```

# Physical Anhedonia Scale
```{r}
# renaming variables
covid_data <- covid_data %>%
  rename(PhAnS_1 = PAS_1_1,
         PhAnS_2 = PAS_2_1,
         PhAnS_3 = PAS_3_1,
         PhAnS_4 = PAS_4_1,
         PhAnS_5 = PAS_5_1,
         PhAnS_6 = PAS_6_1,
         PhAnS_7 = PAS_7_1,
         PhAnS_8 = PAS_8_1,
         PhAnS_9 = PAS_9_1,
         PhAnS_10 = PAS_10_1,
         PhAnS_11 = PAS_11_1,
         PhAnS_12 = PAS_12_1,
         PhAnS_13 = PAS_13_1,
         PhAnS_14 = PAS_14_1,
         PhAnS_15 = PAS_15_1)
```

```{r}
# recoding 
covid_data <- covid_data %>%
  mutate(PhAnS_5 = fct_recode(PhAnS_5, "0" = "2"),
         PhAnS_6 = fct_recode(PhAnS_6, "0" = "2"),
         PhAnS_8 = fct_recode(PhAnS_8, "0" = "2"),
         PhAnS_10 = fct_recode(PhAnS_10, "0" = "2"),
         PhAnS_1 = fct_recode(PhAnS_1, "0" = "1", "1" = "2"),
         PhAnS_2 = fct_recode(PhAnS_2, "0" = "1", "1" = "2"),
         PhAnS_3 = fct_recode(PhAnS_3, "0" = "1", "1" = "2"),
         PhAnS_4 = fct_recode(PhAnS_4, "0" = "1", "1" = "2"),
         PhAnS_7 = fct_recode(PhAnS_7, "0" = "1", "1" = "2"),
         PhAnS_9 = fct_recode(PhAnS_9, "0" = "1", "1" = "2"),
         PhAnS_11 = fct_recode(PhAnS_11, "0" = "1", "1" = "2"),
         PhAnS_12 = fct_recode(PhAnS_12, "0" = "1", "1" = "2"),
         PhAnS_13 = fct_recode(PhAnS_13, "0" = "1", "1" = "2"),
         PhAnS_14 = fct_recode(PhAnS_14, "0" = "1", "1" = "2"),
         PhAnS_15 = fct_recode(PhAnS_15, "0" = "1", "1" = "2"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(PhAnS_1 = parse_integer(as.character(PhAnS_1)),
         PhAnS_2 = parse_integer(as.character(PhAnS_2)),
         PhAnS_3 = parse_integer(as.character(PhAnS_3)),
         PhAnS_4 = parse_integer(as.character(PhAnS_4)),
         PhAnS_5 = parse_integer(as.character(PhAnS_5)),
         PhAnS_6 = parse_integer(as.character(PhAnS_6)),
         PhAnS_7 = parse_integer(as.character(PhAnS_7)),
         PhAnS_8 = parse_integer(as.character(PhAnS_8)),
         PhAnS_9 = parse_integer(as.character(PhAnS_9)),
         PhAnS_10 = parse_integer(as.character(PhAnS_10)),
         PhAnS_11 = parse_integer(as.character(PhAnS_11)),
         PhAnS_12 = parse_integer(as.character(PhAnS_12)),
         PhAnS_13 = parse_integer(as.character(PhAnS_13)),
         PhAnS_14 = parse_integer(as.character(PhAnS_14)),
         PhAnS_15 = parse_integer(as.character(PhAnS_15)))
covid_data <- covid_data %>%
  mutate(PhAnS_score = PhAnS_1 + PhAnS_2 + PhAnS_3 + PhAnS_4 + PhAnS_5 + PhAnS_6 + PhAnS_7 + PhAnS_8 + PhAnS_9 +
           PhAnS_10 + PhAnS_11 + PhAnS_12 + PhAnS_13 + PhAnS_14 + PhAnS_15)
```

# Overall Schizotypy Scores 
```{r}
covid_data <- covid_data %>%
  mutate(pos_sxtypy_total = PAS_total + MIS_total,
         neg_sxtypy_total = Social_Anhedonia_Score + PhAnS_score,
         overall_sxtypy_total = pos_sxtypy_total + neg_sxtypy_total)
```

# STAIT
```{r}
# recoding reverse scored questions
covid_data <- covid_data %>%
  mutate(STAIT_1 = fct_recode(STAIT_1, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_3 = fct_recode(STAIT_3, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_6 = fct_recode(STAIT_6, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_7 = fct_recode(STAIT_7, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_10 = fct_recode(STAIT_10, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_13 = fct_recode(STAIT_13, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_14 = fct_recode(STAIT_14, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_16 = fct_recode(STAIT_16, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIT_19 = fct_recode(STAIT_19, "4" = "1", "3" = "2", "2" = "3", "1" = "4"))
```

```{r}
# scoring
covid_data <- covid_data %>%
   mutate(STAIT_1 = parse_integer(as.character(STAIT_1)),
          STAIT_2 = parse_integer(as.character(STAIT_2)),
          STAIT_3 = parse_integer(as.character(STAIT_3)),
          STAIT_4 = parse_integer(as.character(STAIT_4)),
          STAIT_5 = parse_integer(as.character(STAIT_5)),
          STAIT_6 = parse_integer(as.character(STAIT_6)),
          STAIT_7 = parse_integer(as.character(STAIT_7)),
          STAIT_8 = parse_integer(as.character(STAIT_8)),
          STAIT_9 = parse_integer(as.character(STAIT_9)),
          STAIT_10 = parse_integer(as.character(STAIT_10)),
          STAIT_11 = parse_integer(as.character(STAIT_11)),
          STAIT_12 = parse_integer(as.character(STAIT_12)),
          STAIT_13 = parse_integer(as.character(STAIT_13)),
          STAIT_14 = parse_integer(as.character(STAIT_14)),
          STAIT_15 = parse_integer(as.character(STAIT_15)),
          STAIT_16 = parse_integer(as.character(STAIT_16)),
          STAIT_17 = parse_integer(as.character(STAIT_17)),
          STAIT_18 = parse_integer(as.character(STAIT_18)),
          STAIT_19 = parse_integer(as.character(STAIT_19)),
          STAIT_20 = parse_integer(as.character(STAIT_20)))

covid_data <- covid_data %>%
  mutate(STAIT_total = STAIT_1 + STAIT_2 + STAIT_3 + STAIT_4 + STAIT_5 + STAIT_6 + STAIT_7 + 
           STAIT_8 + STAIT_9 + STAIT_10 + STAIT_11 + STAIT_12 + STAIT_13 + STAIT_14 + STAIT_15 +
           STAIT_16 + STAIT_17 + STAIT_18 + STAIT_19 + STAIT_20)
```

# STAIS
```{r}
# recoding reverse scored questions
covid_data <- covid_data %>%
  mutate(STAIS_1 = fct_recode(STAIS_1, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_2 = fct_recode(STAIS_2, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_5 = fct_recode(STAIS_5, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_8 = fct_recode(STAIS_8, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_10 = fct_recode(STAIS_10, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_11 = fct_recode(STAIS_11, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_15 = fct_recode(STAIS_15, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_16 = fct_recode(STAIS_16, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_19 = fct_recode(STAIS_19, "4" = "1", "3" = "2", "2" = "3", "1" = "4"),
         STAIS_20 = fct_recode(STAIS_20, "4" = "1", "3" = "2", "2" = "3", "1" = "4"))
```

```{r}
# scoring
covid_data <- covid_data %>%
   mutate(STAIS_1 = parse_integer(as.character(STAIS_1)),
          STAIS_2 = parse_integer(as.character(STAIS_2)),
          STAIS_3 = parse_integer(as.character(STAIS_3)),
          STAIS_4 = parse_integer(as.character(STAIS_4)),
          STAIS_5 = parse_integer(as.character(STAIS_5)),
          STAIS_6 = parse_integer(as.character(STAIS_6)),
          STAIS_7 = parse_integer(as.character(STAIS_7)),
          STAIS_8 = parse_integer(as.character(STAIS_8)),
          STAIS_9 = parse_integer(as.character(STAIS_9)),
          STAIS_10 = parse_integer(as.character(STAIS_10)),
          STAIS_11 = parse_integer(as.character(STAIS_11)),
          STAIS_12 = parse_integer(as.character(STAIS_12)),
          STAIS_13 = parse_integer(as.character(STAIS_13)),
          STAIS_14 = parse_integer(as.character(STAIS_14)),
          STAIS_15 = parse_integer(as.character(STAIS_15)),
          STAIS_16 = parse_integer(as.character(STAIS_16)),
          STAIS_17 = parse_integer(as.character(STAIS_17)),
          STAIS_18 = parse_integer(as.character(STAIS_18)),
          STAIS_19 = parse_integer(as.character(STAIS_19)),
          STAIS_20 = parse_integer(as.character(STAIS_20)))

covid_data <- covid_data %>%
  mutate(STAIS_total = STAIS_1 + STAIS_2 + STAIS_3 + STAIS_4 + STAIS_5 + STAIS_6 + STAIS_7 + 
           STAIS_8 + STAIS_9 + STAIS_10 + STAIS_11 + STAIS_12 + STAIS_13 + STAIS_14 + STAIS_15 +
           STAIS_16 + STAIS_17 + STAIS_18 + STAIS_19 + STAIS_20)
```

# PSWQ 
```{r}
# recoding reverse scored questions
covid_data <- covid_data %>%
  mutate(PSWQ_1 = fct_recode(PSWQ_1, "5" = "1", "4" = "2", "3" = "3", "2" = "4", "1" = "5"),
         PSWQ_3 = fct_recode(PSWQ_3, "5" = "1", "4" = "2", "3" = "3", "2" = "4", "1" = "5"),
         PSWQ_8 = fct_recode(PSWQ_8, "5" = "1", "4" = "2", "3" = "3", "2" = "4", "1" = "5"),
         PSWQ_10 = fct_recode(PSWQ_10, "5" = "1", "4" = "2", "3" = "3", "2" = "4", "1" = "5"),
         PSWQ_11 = fct_recode(PSWQ_11, "5" = "1", "4" = "2", "3" = "3", "2" = "4", "1" = "5"))
```

```{r}
# scoring
covid_data <- covid_data %>%
   mutate(PSWQ_1 = parse_integer(as.character(PSWQ_1)),
          PSWQ_2 = parse_integer(as.character(PSWQ_2)),
          PSWQ_3 = parse_integer(as.character(PSWQ_3)),
          PSWQ_4 = parse_integer(as.character(PSWQ_4)),
          PSWQ_5 = parse_integer(as.character(PSWQ_5)),
          PSWQ_6 = parse_integer(as.character(PSWQ_6)),
          PSWQ_7 = parse_integer(as.character(PSWQ_7)),
          PSWQ_8 = parse_integer(as.character(PSWQ_8)),
          PSWQ_9 = parse_integer(as.character(PSWQ_9)),
          PSWQ_10 = parse_integer(as.character(PSWQ_10)),
          PSWQ_11 = parse_integer(as.character(PSWQ_11)),
          PSWQ_12 = parse_integer(as.character(PSWQ_12)),
          PSWQ_13 = parse_integer(as.character(PSWQ_13)),
          PSWQ_14 = parse_integer(as.character(PSWQ_14)),
          PSWQ_15 = parse_integer(as.character(PSWQ_15)),
          PSWQ_16 = parse_integer(as.character(PSWQ_16)))

covid_data <- covid_data %>%
  mutate(PSWQ_total = PSWQ_1 + PSWQ_2 + PSWQ_3 + PSWQ_4 + PSWQ_5 + PSWQ_6 + PSWQ_7 + PSWQ_8 +
           PSWQ_9 + PSWQ_10 + PSWQ_11 + PSWQ_12 + PSWQ_13 + PSWQ_14 + PSWQ_15 + PSWQ_16) 
```


# COVID Conspiracy Beliefs Questions

```{r} 
# renaming (not on SPSS but formatted weird on R)
covid_data <- covid_data %>%
  rename(COVID_19_3_1 = `COVID-19_3_1`,
         COVID_19_3_2 = `COVID-19_3_2`,
         COVID_19_3_3 = `COVID-19_3_3`,
         COVID_19_3_4 = `COVID-19_3_4`,
         COVID_19_3_5 = `COVID-19_3_5`,
         COVID_19_3_6 = `COVID-19_3_6`,
         COVID_19_3_7 = `COVID-19_3_7`,
         COVID_19_3_8 = `COVID-19_3_8`,
         COVID_19_3_9 = `COVID-19_3_9`,
         COVID_19_3_10 = `COVID-19_3_10`,
         COVID_19_3_11 = `COVID-19_3_11`,
         COVID_19_3_12 = `COVID-19_3_12`,
         COVID_19_3_13 = `COVID-19_3_13`,
         COVID_19_3_14 = `COVID-19_3_14`,
         COVID_19_3_15 = `COVID-19_3_15`,
         COVID_19_3_16 = `COVID-19_3_16`)
```

```{r}
# recoding variables
covid_data <- covid_data %>%
   mutate(COVID_19_3_1 = fct_recode(COVID_19_3_1, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_2 = fct_recode(COVID_19_3_2, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_3 = fct_recode(COVID_19_3_3, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_4 = fct_recode(COVID_19_3_4, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_5 = fct_recode(COVID_19_3_5, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_6 = fct_recode(COVID_19_3_6, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_7 = fct_recode(COVID_19_3_7, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_8 = fct_recode(COVID_19_3_8, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_9 = fct_recode(COVID_19_3_9, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_10 = fct_recode(COVID_19_3_10, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_11 = fct_recode(COVID_19_3_11, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_12 = fct_recode(COVID_19_3_12, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_13 = fct_recode(COVID_19_3_13, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_14 = fct_recode(COVID_19_3_14, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_15 = fct_recode(COVID_19_3_15, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6"),
          COVID_19_3_16 = fct_recode(COVID_19_3_16, "1" = "2", "2" = "3", "3" = "4", "4" = "5", "5" = "6")) %>%
  mutate(COVID_19_3_1_true = fct_recode(COVID_19_3_1, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_2_true = fct_recode(COVID_19_3_2, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_3_true = fct_recode(COVID_19_3_3, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_4_true = fct_recode(COVID_19_3_4, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_5_true = fct_recode(COVID_19_3_5, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_6_true = fct_recode(COVID_19_3_6, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_7_true = fct_recode(COVID_19_3_7, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_8_true = fct_recode(COVID_19_3_8, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_9_true = fct_recode(COVID_19_3_9, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_10_true = fct_recode(COVID_19_3_10, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_11_true = fct_recode(COVID_19_3_11, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_12_true = fct_recode(COVID_19_3_12, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_13_true = fct_recode(COVID_19_3_13, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_14_true = fct_recode(COVID_19_3_14, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_15_true = fct_recode(COVID_19_3_15, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"),
         COVID_19_3_16_true = fct_recode(COVID_19_3_16, "0" = "1", "0" = "2", "0" = "3", "1" = "4", "1" = "5"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(COVID_19_3_1 = parse_integer(as.character(COVID_19_3_1)),
         COVID_19_3_2 = parse_integer(as.character(COVID_19_3_2)),
         COVID_19_3_3 = parse_integer(as.character(COVID_19_3_3)),
         COVID_19_3_4 = parse_integer(as.character(COVID_19_3_4)),
         COVID_19_3_5 = parse_integer(as.character(COVID_19_3_5)),
         COVID_19_3_6 = parse_integer(as.character(COVID_19_3_6)),
         COVID_19_3_7 = parse_integer(as.character(COVID_19_3_7)),
         COVID_19_3_8 = parse_integer(as.character(COVID_19_3_8)),
         COVID_19_3_9 = parse_integer(as.character(COVID_19_3_9)),
         COVID_19_3_10 = parse_integer(as.character(COVID_19_3_10)),
         COVID_19_3_11 = parse_integer(as.character(COVID_19_3_11)),
         COVID_19_3_12 = parse_integer(as.character(COVID_19_3_12)),
         COVID_19_3_13 = parse_integer(as.character(COVID_19_3_13)),
         COVID_19_3_14 = parse_integer(as.character(COVID_19_3_14)),
         COVID_19_3_15 = parse_integer(as.character(COVID_19_3_15)),
         COVID_19_3_16 = parse_integer(as.character(COVID_19_3_16)),
         COVID_19_3_1_true = parse_integer(as.character(COVID_19_3_1_true)),
         COVID_19_3_2_true = parse_integer(as.character(COVID_19_3_2_true)),
         COVID_19_3_3_true = parse_integer(as.character(COVID_19_3_3_true)),
         COVID_19_3_4_true = parse_integer(as.character(COVID_19_3_4_true)),
         COVID_19_3_5_true = parse_integer(as.character(COVID_19_3_5_true)),
         COVID_19_3_6_true = parse_integer(as.character(COVID_19_3_6_true)),
         COVID_19_3_7_true = parse_integer(as.character(COVID_19_3_7_true)),
         COVID_19_3_8_true = parse_integer(as.character(COVID_19_3_8_true)),
         COVID_19_3_9_true = parse_integer(as.character(COVID_19_3_9_true)),
         COVID_19_3_10_true = parse_integer(as.character(COVID_19_3_10_true)),
         COVID_19_3_11_true = parse_integer(as.character(COVID_19_3_11_true)),
         COVID_19_3_12_true = parse_integer(as.character(COVID_19_3_12_true)),
         COVID_19_3_13_true = parse_integer(as.character(COVID_19_3_13_true)),
         COVID_19_3_14_true = parse_integer(as.character(COVID_19_3_14_true)),
         COVID_19_3_15_true = parse_integer(as.character(COVID_19_3_15_true)),
         COVID_19_3_16_true = parse_integer(as.character(COVID_19_3_16_true))) 

covid_data <- covid_data %>%
  mutate(COVID_conspiracies_total = rowMeans(subset(covid_data, select = c(COVID_19_3_1, COVID_19_3_2, COVID_19_3_3,
             COVID_19_3_4, COVID_19_3_5, COVID_19_3_6, COVID_19_3_7, COVID_19_3_8, COVID_19_3_9, COVID_19_3_10,
             COVID_19_3_11, COVID_19_3_12, COVID_19_3_13, COVID_19_3_14, COVID_19_3_15, COVID_19_3_16), na.rm = TRUE)),
         Conspiracies_endorsed = COVID_19_3_1_true + COVID_19_3_2_true + COVID_19_3_3_true + COVID_19_3_4_true + 
             COVID_19_3_5_true + COVID_19_3_6_true + COVID_19_3_7_true + COVID_19_3_8_true + COVID_19_3_9_true +
             COVID_19_3_10_true + COVID_19_3_11_true + COVID_19_3_12_true + COVID_19_3_13_true + COVID_19_3_14_true +
             COVID_19_3_15_true + COVID_19_3_16_true,
         Conspiracies_endorsed_lgtrans = log(Conspiracies_endorsed + 1))
```

# COVID 19 Facts v Misinfo

```{r}
# renaming (not on SPSS but they formatted weird on R)
covid_data <- covid_data %>%
  rename(Facts_vs_misinfo_1 = `Facts vs misinfo_1`,
         Facts_vs_misinfo_2 = `Facts vs misinfo_2`,
         Facts_vs_misinfo_3 = `Facts vs misinfo_3`,
         Facts_vs_misinfo_4 = `Facts vs misinfo_4`,
         Facts_vs_misinfo_5 = `Facts vs misinfo_5`,
         Facts_vs_misinfo_6 = `Facts vs misinfo_6`,
         Facts_vs_misinfo_7 = `Facts vs misinfo_7`,
         Facts_vs_misinfo_8 = `Facts vs misinfo_8`,
         Facts_vs_misinfo_9 = `Facts vs misinfo_9`,
         Facts_vs_misinfo_10 = `Facts vs misinfo_10`,
         Facts_vs_misinfo_11 = `Facts vs misinfo_11`,
         Facts_vs_misinfo_12 = `Facts vs misinfo_12`,
         Facts_vs_misinfo_13 = `Facts vs misinfo_13`,
         Facts_vs_misinfo_14 = `Facts vs misinfo_14`,
         Facts_vs_misinfo_15 = `Facts vs misinfo_15`,
         Facts_vs_misinfo_16 = `Facts vs misinfo_16`)
```

```{r}
# recoding facts v misinfo
covid_data <- covid_data %>%
  mutate(Facts_vs_misinfo_2 = fct_recode(Facts_vs_misinfo_2, "0" = "2"),
         Facts_vs_misinfo_5 = fct_recode(Facts_vs_misinfo_5, "0" = "2"),
         Facts_vs_misinfo_7 = fct_recode(Facts_vs_misinfo_7, "0" = "2"),
         Facts_vs_misinfo_11 = fct_recode(Facts_vs_misinfo_11, "0" = "2"),
         Facts_vs_misinfo_1 = fct_recode(Facts_vs_misinfo_1, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_3 = fct_recode(Facts_vs_misinfo_3, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_4 = fct_recode(Facts_vs_misinfo_4, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_6 = fct_recode(Facts_vs_misinfo_6, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_8 = fct_recode(Facts_vs_misinfo_8, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_9 = fct_recode(Facts_vs_misinfo_9, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_10 = fct_recode(Facts_vs_misinfo_10, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_12 = fct_recode(Facts_vs_misinfo_12, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_13 = fct_recode(Facts_vs_misinfo_13, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_14 = fct_recode(Facts_vs_misinfo_14, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_15 = fct_recode(Facts_vs_misinfo_15, "0" = "1", "1" = "2"),
         Facts_vs_misinfo_16 = fct_recode(Facts_vs_misinfo_16, "0" = "1", "1" = "2"))
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(Facts_vs_misinfo_1 = parse_integer(as.character(Facts_vs_misinfo_1)),
         Facts_vs_misinfo_2 = parse_integer(as.character(Facts_vs_misinfo_2)),
         Facts_vs_misinfo_3 = parse_integer(as.character(Facts_vs_misinfo_3)),
         Facts_vs_misinfo_4 = parse_integer(as.character(Facts_vs_misinfo_4)),
         Facts_vs_misinfo_5 = parse_integer(as.character(Facts_vs_misinfo_5)),
         Facts_vs_misinfo_6 = parse_integer(as.character(Facts_vs_misinfo_6)),
         Facts_vs_misinfo_7 = parse_integer(as.character(Facts_vs_misinfo_7)),
         Facts_vs_misinfo_8 = parse_integer(as.character(Facts_vs_misinfo_8)),
         Facts_vs_misinfo_9 = parse_integer(as.character(Facts_vs_misinfo_9)),
         Facts_vs_misinfo_10 = parse_integer(as.character(Facts_vs_misinfo_10)),
         Facts_vs_misinfo_11 = parse_integer(as.character(Facts_vs_misinfo_11)),
         Facts_vs_misinfo_12 = parse_integer(as.character(Facts_vs_misinfo_12)),
         Facts_vs_misinfo_13 = parse_integer(as.character(Facts_vs_misinfo_13)),
         Facts_vs_misinfo_14 = parse_integer(as.character(Facts_vs_misinfo_14)),
         Facts_vs_misinfo_15 = parse_integer(as.character(Facts_vs_misinfo_15)),
         Facts_vs_misinfo_16 = parse_integer(as.character(Facts_vs_misinfo_16))) %>%
  mutate(COVID_factsvmisinfo_score = Facts_vs_misinfo_1 + Facts_vs_misinfo_2 + Facts_vs_misinfo_3 + Facts_vs_misinfo_4 +
           Facts_vs_misinfo_5 + Facts_vs_misinfo_6 + Facts_vs_misinfo_7 + Facts_vs_misinfo_8 + Facts_vs_misinfo_9 + 
           Facts_vs_misinfo_10 + Facts_vs_misinfo_11 + Facts_vs_misinfo_12 + Facts_vs_misinfo_13 + Facts_vs_misinfo_14 +
           Facts_vs_misinfo_15 + Facts_vs_misinfo_16)
```

# COVID 19 Health Behavior
```{r}
# renaming variables
covid_data <- covid_data %>%
  rename(Health_Behavior_1 = Health_Behavior,
         Health_Behavior_1a = Health_Behavior_1,
         Health_Behavior_2 = Health_Behavior_2,
         Health_Behavior_2a = Health_Behavior_3,
         Health_Behavior_3 = Health_Behavior_4,
         Health_Behavior_4 = Health_Behavior_5,
         Health_Behavior_5 = Health_Behavior_6,
         Health_Behavior_6 = Health_Behavior_7,
         Health_Behavior_7 = Health_Behavior_8,
         Health_Behavior_8 = Health_Behavior_9,
         Health_Behavior_9 = Health_Behavior_10)
```

```{r}
# scoring
covid_data <- covid_data %>%
  mutate(Health_Behavior_1 = parse_integer(Health_Behavior_1),
         Health_Behavior_1a = parse_integer(Health_Behavior_1a),
         Health_Behavior_2 = parse_integer(Health_Behavior_2),
         Health_Behavior_2a = parse_integer(Health_Behavior_2a),
         Health_Behavior_3 = parse_integer(Health_Behavior_3),
         Health_Behavior_4 = parse_integer(Health_Behavior_4),
         Health_Behavior_5 = parse_integer(Health_Behavior_5),
         Health_Behavior_6 = parse_integer(Health_Behavior_6),
         Health_Behavior_7 = parse_integer(Health_Behavior_7),
         Health_Behavior_8 = parse_integer(Health_Behavior_8),
         Health_Behavior_9 = parse_integer(Health_Behavior_9)) %>%
  mutate(Health_Behavior_Score = Health_Behavior_1 + Health_Behavior_1a + Health_Behavior_2 + 
           Health_Behavior_2a + Health_Behavior_3 + Health_Behavior_4 + Health_Behavior_5 + Health_Behavior_6 +
           Health_Behavior_7 + Health_Behavior_8)
```

# COVID Predicted Consequences
```{r}
# renaming variables
covid_data <- covid_data %>%
  rename(COVID_19_2_1_Headache = "COVID-19_2_1",
         COVID_19_2_1_Fever = "COVID-19_2_2",
         COVID_19_2_1_Bodyache = "COVID-19_2_3",
         COVID_19_2_1_Fatigue= "COVID-19_2_4",
         COVID_19_2_1_Neckpain = "COVID-19_2_5",
         COVID_19_2_1_Lossofsleep = "COVID-19_2_6",
         COVID_19_2_1_Lossofappetite = "COVID-19_2_7",
         COVID_19_2_1_Cough = "COVID-19_2_8",
         COVID_19_2_1_Sorethroat = "COVID-19_2_9",
         COVID_19_2_1_Nasalcongestion = "COVID-19_2_10",
         COVID_19_2_1_Breathingproblems = "COVID-19_2_11",
         COVID_19_2_2_getoutofbed = "COVID-19_2_1_1",
         COVID_19_2_2_preparemeals = "COVID-19_2_2_1",
         COVID_19_2_2_performdailyroutines = "COVID-19_2_3_1",
         COVID_19_2_2_leavehome = "COVID-19_2_4_1",
         COVID_19_2_2_concentrateonwork = "COVID-19_2_5_1",
         COVID_19_2_2_completemywork = "COVID-19_2_6_1",
         COVID_19_2_Irritable = "COVID-19_2_1_2",
         COVID_19_2_Helpless = "COVID-19_2_2_2",
         COVID_19_2_Worried = "COVID-19_2_3_2",
         COVID_19_2_Frustrated = "COVID-19_2_4_2",
         COVID_19_2_makingthemworry= "COVID-19_2_1_3",
         COVID_19_2_beingaburden = "COVID-19_2_2_3",
         COVID_19_2_limitingtheirlives = "COVID-19_2_3_3",
         COVID_19_2_needingtodependonthem = "COVID-19_2_4_3",
         COVID_19_2_takecareofpeople = "COVID-19_2_5_2",
         COVID_19_2_spreadinginfectiontothem = "COVID-19_2_6_2",
         COVID_19_2_sufferfinancially = "COVID-19_2_1_4",
         COVID_19_2_personalrelationships = "COVID-19_2_2_4",
         COVID_19_2_foodandhousing = "COVID-19_2_3_4")
  
```

```{r}
# Scoring COVID Consequences variables
class(covid_data$COVID_19_2_takecareofpeople)
covid_data <- covid_data %>%
  mutate(COVID_19_2_1_Headache = parse_integer(as.character(COVID_19_2_1_Headache)),
         COVID_19_2_1_Fever = parse_integer(as.character(COVID_19_2_1_Fever)),
         COVID_19_2_1_Bodyache = parse_integer(as.character(COVID_19_2_1_Bodyache)),
         COVID_19_2_1_Fatigue = parse_integer(as.character(COVID_19_2_1_Fatigue)),
         COVID_19_2_1_Neckpain = parse_integer(as.character(COVID_19_2_1_Neckpain)),
         COVID_19_2_1_Lossofsleep = parse_integer(as.character(COVID_19_2_1_Lossofsleep)),                               
         COVID_19_2_1_Lossofappetite = parse_integer(as.character(COVID_19_2_1_Lossofappetite)), 
         COVID_19_2_1_Cough = parse_integer(as.character(COVID_19_2_1_Cough)),
         COVID_19_2_1_Sorethroat = parse_integer(as.character(COVID_19_2_1_Sorethroat)),
         COVID_19_2_1_Nasalcongestion = parse_integer(as.character(COVID_19_2_1_Nasalcongestion)),
         COVID_19_2_1_Breathingproblems = parse_integer(as.character(COVID_19_2_1_Breathingproblems)),
         COVID_19_2_2_getoutofbed = parse_integer(as.character(COVID_19_2_2_getoutofbed)),
         COVID_19_2_2_preparemeals = parse_integer(as.character(COVID_19_2_2_preparemeals)),
         COVID_19_2_2_performdailyroutines = parse_integer(as.character(COVID_19_2_2_performdailyroutines)),  
         COVID_19_2_2_leavehome = parse_integer(as.character(COVID_19_2_2_leavehome)), 
         COVID_19_2_2_concentrateonwork = parse_integer(as.character(COVID_19_2_2_concentrateonwork)),
         COVID_19_2_2_completemywork = parse_integer(as.character(COVID_19_2_2_completemywork)),  
         COVID_19_2_Irritable = parse_integer(as.character(COVID_19_2_Irritable)),                       
         COVID_19_2_Worried = parse_integer(as.character(COVID_19_2_Worried)),
         COVID_19_2_Helpless = parse_integer(as.character(COVID_19_2_Helpless)),
         COVID_19_2_Frustrated = parse_integer(as.character(COVID_19_2_Frustrated)),                                               COVID_19_2_makingthemworry = parse_integer(as.character(COVID_19_2_makingthemworry)),
         COVID_19_2_beingaburden = parse_integer(as.character(COVID_19_2_beingaburden)),
         COVID_19_2_limitingtheirlives = parse_integer(as.character(COVID_19_2_limitingtheirlives)),
         COVID_19_2_needingtodependonthem = parse_integer(as.character(COVID_19_2_needingtodependonthem)),
         COVID_19_2_takecareofpeople = parse_integer(as.character(COVID_19_2_takecareofpeople)),
         COVID_19_2_spreadinginfectiontothem = parse_integer(as.character(COVID_19_2_spreadinginfectiontothem)),
         COVID_19_2_sufferfinancially = parse_integer(as.character(COVID_19_2_sufferfinancially)),
         COVID_19_2_personalrelationships = parse_integer(as.character(COVID_19_2_personalrelationships)),
         COVID_19_2_foodandhousing = parse_integer(as.character(COVID_19_2_foodandhousing)))                                     
covid_data <- covid_data %>%                                        
  mutate(COVID_conseq_sxs = COVID_19_2_1_Headache + COVID_19_2_1_Fever + COVID_19_2_1_Bodyache + COVID_19_2_1_Fatigue +
              COVID_19_2_1_Neckpain + COVID_19_2_1_Lossofsleep + COVID_19_2_1_Lossofappetite + COVID_19_2_1_Cough + 
              COVID_19_2_1_Sorethroat + COVID_19_2_1_Nasalcongestion + COVID_19_2_1_Breathingproblems,
         COVID_conseq_abilities = COVID_19_2_2_getoutofbed + COVID_19_2_2_preparemeals + COVID_19_2_2_performdailyroutines +
              COVID_19_2_2_leavehome + COVID_19_2_2_concentrateonwork + COVID_19_2_2_completemywork,
         COVID_conseq_mood = COVID_19_2_Irritable + COVID_19_2_Worried + COVID_19_2_Helpless + COVID_19_2_Frustrated,
         COVID_conseq_burden_to_others = COVID_19_2_makingthemworry + COVID_19_2_beingaburden + COVID_19_2_limitingtheirlives +
              COVID_19_2_needingtodependonthem + COVID_19_2_takecareofpeople + COVID_19_2_spreadinginfectiontothem,
         COVID_conseq_realworld = COVID_19_2_sufferfinancially + COVID_19_2_personalrelationships + COVID_19_2_foodandhousing,
         COVID_conseq_total = COVID_conseq_sxs + COVID_conseq_abilities + COVID_conseq_mood + COVID_conseq_burden_to_others +
              COVID_conseq_realworld)
```

# Perceived Vulnerability to Disease Scale 

```{r}
# Recoding reversed scoring questions
covid_data <- covid_data %>%
  mutate(PVDS_3 = fct_recode(PVDS_3,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"),
         PVDS_5 = fct_recode(PVDS_5,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"),
         PVDS_11 = fct_recode(PVDS_11,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"),
         PVDS_12 = fct_recode(PVDS_12,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"),
         PVDS_13 = fct_recode(PVDS_13,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"),
         PVDS_14 = fct_recode(PVDS_14,
                             "7" = "1", "6" = "2", "5" = "3", "4" = "4", "3" = "5", "2" = "6", "1" = "7"))
```

```{r}
# Computing PVDS Scores
covid_data <- covid_data %>%
    mutate(PVDS_1 = parse_integer(as.character(PVDS_1)),
           PVDS_2 = parse_integer(as.character(PVDS_2)),
           PVDS_3 = parse_integer(as.character(PVDS_3)),
           PVDS_4 = parse_integer(as.character(PVDS_4)),
           PVDS_5 = parse_integer(as.character(PVDS_5)),
           PVDS_6 = parse_integer(as.character(PVDS_6)),
           PVDS_7 = parse_integer(as.character(PVDS_7)),
           PVDS_8 = parse_integer(as.character(PVDS_8)),
           PVDS_9 = parse_integer(as.character(PVDS_9)),
           PVDS_10 = parse_integer(as.character(PVDS_10)),
           PVDS_11 = parse_integer(as.character(PVDS_11)),
           PVDS_12 = parse_integer(as.character(PVDS_12)),
           PVDS_13 = parse_integer(as.character(PVDS_13)),
           PVDS_14 = parse_integer(as.character(PVDS_14)),
           PVDS_15 = parse_integer(as.character(PVDS_15))) 

covid_data <- covid_data %>%
  mutate(Perceived_Infectability = rowMeans(subset(covid_data, select = c(PVDS_8, PVDS_12, PVDS_2, PVDS_14, PVDS_10, PVDS_5, PVDS_6), na.rm = TRUE)),
         Germ_Aversion = rowMeans(subset(covid_data, select = c(PVDS_7, PVDS_15, PVDS_4, PVDS_9, PVDS_3, PVDS_13, PVDS_11), na.rm = TRUE)))
```


# Rotters Locus of Control Variables 
```{r}
# Renaming RLOC variables
covid_data <- covid_data %>%
  rename(RLOC_1 = QID106,
         RLOC_2 = QID107,
         RLOC_3 = QID108,
         RLOC_4 = QID109,
         RLOC_5 = QID110,
         RLOC_6 = QID111,
         RLOC_7 = QID112,
         RLOC_8 = QID113,
         RLOC_9 = QID114,
         RLOC_10 = QID135,
         RLOC_11 = QID136,
         RLOC_12 = QID137,
         RLOC_13 = QID138,
         RLOC_14 = QID139,
         RLOC_15 = QID140,
         RLOC_16 = QID141,
         RLOC_17 = QID142,
         RLOC_18 = QID143,
         RLOC_19 = QID144,
         RLOC_20 = QID145,
         RLOC_21 = QID146,
         RLOC_22 = QID147,
         RLOC_23 = QID148,
         RLOC_24 = QID149,
         RLOC_25 = QID150,
         RLOC_26 = QID151,
         RLOC_27 = QID152,
         RLOC_28 = QID153,
         RLOC_29 = QID154)
```

```{r}
# Recoding RLOC variables
covid_data <- covid_data %>%
  mutate(RLOC_2 = fct_recode(RLOC_2, "1" = "1", "0" = "2"),
                RLOC_6 = fct_recode(RLOC_6, "1" = "1", "0" = "2"),
                RLOC_7 = fct_recode(RLOC_7, "1" = "1", "0" = "2"),
                RLOC_9 = fct_recode(RLOC_9, "1" = "1", "0" = "2"),
                RLOC_16 = fct_recode(RLOC_16, "1" = "1", "0" = "2"),
                RLOC_17 = fct_recode(RLOC_17, "1" = "1", "0" = "2"),
                RLOC_18 = fct_recode(RLOC_18, "1" = "1", "0" = "2"),
                RLOC_20 = fct_recode(RLOC_20, "1" = "1", "0" = "2"),
                RLOC_21 = fct_recode(RLOC_21, "1" = "1", "0" = "2"),
                RLOC_23 = fct_recode(RLOC_23, "1" = "1", "0" = "2"),
                RLOC_25 = fct_recode(RLOC_25, "1" = "1", "0" = "2"),
                RLOC_29 = fct_recode(RLOC_29, "1" = "1", "0" = "2"),
                RLOC_3 = fct_recode(RLOC_3, "0" = "1", "1" = "2"),
                RLOC_4 = fct_recode(RLOC_4, "0" = "1", "1" = "2"),
                RLOC_5 = fct_recode(RLOC_5, "0" = "1", "1" = "2"), 
                RLOC_10 = fct_recode(RLOC_10, "0" = "1", "1" = "2"), 
                RLOC_11 = fct_recode(RLOC_11, "0" = "1", "1" = "2"),
                RLOC_12 = fct_recode(RLOC_12, "0" = "1", "1" = "2"),
                RLOC_13 = fct_recode(RLOC_13, "0" = "1", "1" = "2"),
                RLOC_15 = fct_recode(RLOC_15, "0" = "1", "1" = "2"),
                RLOC_22 = fct_recode(RLOC_22, "0" = "1", "1" = "2"),
                RLOC_26 = fct_recode(RLOC_26, "0" = "1", "1" = "2"),
                RLOC_28 = fct_recode(RLOC_28, "0" = "1", "1" = "2"))
```

```{r}
# Computing RLOC Scores
covid_data <- covid_data %>%
  mutate(RLOC_2 = parse_integer(as.character(RLOC_2)),
         RLOC_3 = parse_integer(as.character(RLOC_3)),
         RLOC_4 = parse_integer(as.character(RLOC_4)),
         RLOC_5 = parse_integer(as.character(RLOC_5)),
         RLOC_6 = parse_integer(as.character(RLOC_6)),
         RLOC_7 = parse_integer(as.character(RLOC_7)),
         RLOC_9 = parse_integer(as.character(RLOC_9)),
         RLOC_10 = parse_integer(as.character(RLOC_10)),
         RLOC_11= parse_integer(as.character(RLOC_11)),
         RLOC_12 = parse_integer(as.character(RLOC_12)),
         RLOC_13 = parse_integer(as.character(RLOC_13)),
         RLOC_15 = parse_integer(as.character(RLOC_15)),
         RLOC_16 = parse_integer(as.character(RLOC_16)),
         RLOC_17= parse_integer(as.character(RLOC_17)),
         RLOC_18 = parse_integer(as.character(RLOC_18)),
         RLOC_20 = parse_integer(as.character(RLOC_20)),
         RLOC_21 = parse_integer(as.character(RLOC_21)),
         RLOC_22 = parse_integer(as.character(RLOC_22)),
         RLOC_23 = parse_integer(as.character(RLOC_23)),
         RLOC_25 = parse_integer(as.character(RLOC_25)),
         RLOC_26 = parse_integer(as.character(RLOC_26)),
         RLOC_28 = parse_integer(as.character(RLOC_28)),
         RLOC_29 = parse_integer(as.character(RLOC_29))) %>%
  mutate(Rotters_general = RLOC_5 + RLOC_9 + RLOC_11 + RLOC_13 + RLOC_15 + RLOC_16 + RLOC_18 + RLOC_25 + RLOC_28,
         Rotters_political = RLOC_3 + RLOC_12 + RLOC_17 + RLOC_22,
         RLOC_Total_Score = RLOC_2 + RLOC_3 + RLOC_4 + RLOC_5 + RLOC_6 + RLOC_7 + RLOC_9 + RLOC_10 + RLOC_11 + 
           RLOC_12 + RLOC_13 + RLOC_15 + RLOC_16 + RLOC_17 + RLOC_18 + RLOC_20 + RLOC_21 + RLOC_22 + RLOC_23 + 
           RLOC_25 + RLOC_26 + RLOC_28 + RLOC_29)
```

# Need for Closure Scale 
```{r}
covid_data <- covid_data %>%
  mutate(NFCS_1 = parse_integer(as.character(NFCS_1)),
         NFCS_2 = parse_integer(as.character(NFCS_2)),
         NFCS_3 = parse_integer(as.character(NFCS_3)),
         NFCS_4 = parse_integer(as.character(NFCS_4)),
         NFCS_5 = parse_integer(as.character(NFCS_5)),
         NFCS_6 = parse_integer(as.character(NFCS_6)),
         NFCS_7 = parse_integer(as.character(NFCS_7)),
         NFCS_8 = parse_integer(as.character(NFCS_8)),
         NFCS_9 = parse_integer(as.character(NFCS_9)),
         NFCS_10 = parse_integer(as.character(NFCS_10)),
         NFCS_11 = parse_integer(as.character(NFCS_11)),
         NFCS_12 = parse_integer(as.character(NFCS_12)),
         NFCS_13 = parse_integer(as.character(NFCS_13)),
         NFCS_14 = parse_integer(as.character(NFCS_14)),
         NFCS_15 = parse_integer(as.character(NFCS_15))) %>%
  mutate(NFCS_Total_Score = NFCS_1 + NFCS_2 + NFCS_3 + NFCS_4 + NFCS_5 + NFCS_6 + NFCS_7 + NFCS_8 + NFCS_9 + NFCS_10 + NFCS_11 + NFCS_12 + NFCS_13 + NFCS_14 + NFCS_15)
```

```{r}
write_csv(covid_data, "COVID_19_December_2020_Cleaned_Data.csv")
```

